SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-10-28 docs/questioning.tex
some changes

A malicious user can initiate the attack through two different routes.
The attacker may use the browser of an innocent user as an attack
vehicle, through which the code will be injected in the application.
For example, the attacker could craft a malicious script into a {\sc url}
and then trick an end user to click on it via social engineering (i.e., phishing).
({\sc step}: {\sc p-xss}' 1 \text{\textbar} {\sc n-xss}' 1 \text{\textbar} {\sc csrf} 1).
Alternatively, the attacker may be able to inject
directly the malicious code in the application. For example, consider
a web application that accepts and redisplays user input
without appropriate validation. An attacker could
upload data containing a specially crafted script (for example, in a
blog comment) to steal the cookies of the visiting users or embed
malicious {\sc sql} code to retrieve all the password entries from a
database ({\sc step}: {\sc dsl} 1 \text{\textbar}
{\sc p-xss} 1 \text{\textbar} {\sc n-xss} 1).
Note that an {\sc xss} attack can start from both routes.

@@

Table~\ref{tab:avail} presents
our findings regarding the availability of the mechanism
in terms of: source code and corresponding executables.
We also examined the availability of the testbeds mentioned in the paper.
The check mark (\tick) indicates that at some point within the publication,
there is a homepage where the reader can refer to, to download the
corresponding software. {\sc ao} (Available On-line) suggests that
the software is available on-line but the address was not mentioned
in the paper, which probably indicates that the authors made
it available after the publication. The question mark ({\bf ?}),
indicates that the a homepage for the software was included
in the publication but now it is not available.

Finally, as we mentioned in Subsection~\ref{sec:model},
Figure~\ref{fig:attacks} illustrates in which step
of out attack model the mechanisms detect attacks.

@@

{\sc isr} is a deterministic approach that can be applied
to detect different attacks in an efficient manner.
However, Sovarel et al.~\cite{SEP05}
have investigated thoroughly the effectiveness
of {\sc isr} and showed that a malicious user
may be able to circumvent {\sc isr} by determining
the randomization key and their results
indicate that doing {\sc isr} in a way that
provides a certain degree of security against a motivated
attacker is more difficult than previously thought.

>>>>

A malicious user can initiate the attack through two different routes.
The attacker may use the browser of an innocent user as an attack
vehicle, through which the code will be injected in the application.
For example, the attacker could craft a malicious script into a {\sc url}
and then trick an end user to click on it via social engineering (i.e., phishing ---
{\sc step}: {\sc p-xss}' 1 \text{\textbar} {\sc n-xss}' 1 \text{\textbar} {\sc csrf} 1).
Alternatively, the attacker may be able to inject
directly the malicious code in the application. For example, consider
a web application that accepts and redisplays user input
without appropriate validation. An attacker could
upload data containing a specially crafted script (for example, in a
blog comment) to steal the cookies of the visiting users or embed
malicious {\sc sql} code to retrieve all the password entries from a
database ({\sc step}: {\sc dsl} 1 \text{\textbar}
{\sc p-xss} 1 \text{\textbar} {\sc n-xss} 1).
Note that an {\sc xss} attack can start from both routes.

@@

Table~\ref{tab:avail} presents
our findings regarding the availability of the mechanism
in terms of source code and corresponding executables.
We also examined the availability of the testbeds mentioned in the paper.
The check mark (\tick) indicates that at some point within the publication,
there is a homepage where the reader can refer to, to download the
corresponding software. {\sc ao} (Available On-line) suggests that
the software is available on-line but the address was not mentioned
in the paper, which probably indicates that the authors made
it available after the publication. The question mark ({\bf ?}),
indicates that the a homepage for the software was included
in the publication but now it is not available.

Finally, as we mentioned in Subsection~\ref{sec:model},
Figure~\ref{fig:attacks} illustrates the point where
mechanisms detect attacks.

@@

{\sc isr} is a deterministic approach that can be applied
to detect different attacks in an efficient manner.
However, Sovarel et al.~\cite{SEP05}
have investigated thoroughly the effectiveness
of {\sc isr} and showed that a malicious user
may be able to circumvent it by determining
the randomization key and their results
indicate that doing {\sc isr} in a way that
provides a certain degree of security against a motivated
attacker is more difficult than previously thought.
